Removal and Replacement only

### 2020-08-07 analysis/figure-3.Rmd
typo fix

i <- makebargraph(DEGmanipf, "gonad","DEGs w/ + LFC", 0, 3200, DEGmanipf$comparison) + 
  theme(strip.text = element_blank()) + 
  labs(title = "female hypothalamus",x = "Comparison of manipulated group to parental controls") + 
  scale_x_discrete(breaks= comparisonlevelsmanip,
                      labels= comparisonlabelssmanip,
                   drop=FALSE)
fig3 <- plot_grid(c, a,b,f,d,e,i,g,h, ncol = 3, rel_widths = c(2,1.8,1), 
                  labels = c("A", "", "",
                             "B", "", "",
                             "C", "", ""), label_size = 8, hjust = 0)
fig3

>>>>

i <- makebargraph(DEGmanipf, "gonad","DEGs w/ + LFC", 0, 3200, DEGmanipf$comparison) + 
  theme(strip.text = element_blank()) + 
  labs(title = "female gonads",x = "Comparison of manipulated group to parental controls") + 
  scale_x_discrete(breaks= comparisonlevelsmanip,
                      labels= comparisonlabelssmanip,
                   drop=FALSE)
fig3 <- plot_grid(c, a,b,f,d,e,i,g,h, ncol = 3, rel_widths = c(2,1.8,1), 
                  labels = c("A", "", "",
                             "B", "", "",
                             "C", "", ""), label_size = 8, hjust = 0)
fig3
